---
title: "MYGA Customer Analysis"
author: "Paul Tyler"
date: "April 3, 2016"
output:
  html_document: null
  fig_width: 8
  pdf_document: default
  theme: united
  word_document: default
---
```{r results='asis', echo=FALSE, include=FALSE,}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
#formating tables
library(xtable)

#data wrangling
library(dplyr)
library(ggplot2)
library(tidyr)

#text processing
library(stringi)

```

## Overview

During both MYGA specials, iPipeline retained all answers to suitability questions answered by clients. This gives us a very interesting look into the demographics of these policyholders. The analysis pulls from file with over 600,000 records of all apps submitted through the Affirm platform. Some of the records include cases that may not have been placed and may possibly include some test cases. We will progressively clean the file as we receive better information from Dell and FGL systems.

## Sales Volume

This file includes records of 5,970 applications that represented $532.5 million in premiums. Each sale averaged just under $90,000. The median case size was $50,000. Though we saw a wide range of case sizes, we did see four meaningful clusters at $25,000, $50,000, $100,000 and $150,000.

```{r results='asis', echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

## Preprocess files
#read in suitability data file
allapp <- read.csv(file="FGLDistSuitab.csv", header=TRUE, sep=",")
dell <- read.csv(file = "dell.csv", header=TRUE, sep=",")
fgl <- read.csv(file = "MYGA-append.csv", header=TRUE, sep=",")

#clip and reshape key values into a table
appdata <- subset(allapp, grepl("^SUIT*", allapp$XmlKey))
appdata <- select(appdata, TransIdentifier, XmlKey, XmlValue)
appdata <-spread(appdata, XmlKey, XmlValue)

#appdata[is.na(appdata)] <- 0

#Income & expense analysis - source
appdata <- rename(appdata, Monthly_Income = SUIT42)
#appdata$Monthly_Income <- as.numeric(as.character(appdata$Monthly_Income)
appdata$Monthly_Income <- as.numeric(as.character(appdata$Monthly_Income))

appdata <- rename(appdata, Monthly_Expense = SUIT43)
#appdata$Monthly_Expense <- as.numeric(as.character(appdata$Monthly_Expense))
appdata$Monthly_Expense <- as.numeric(as.character(appdata$Monthly_Expense))
appdata$Monthly_Discretionary <- appdata$Monthly_Income - appdata$Monthly_Expense

#size of policy and funds - source
appdata <- rename(appdata, Liquid_Src = SUIT88)
appdata$Liquid_Src <- as.numeric(as.character(appdata$Liquid_Src))
appdata <- rename(appdata, Non_Liquid_Src = SUIT98)
appdata$Non_Liquid_Src <- as.numeric(as.character(appdata$Non_Liquid_Src))
appdata$Purchase <- appdata$Non_Liquid_Src + appdata$Liquid_Src
appdata$Liquid_Src_Pct <- round(appdata$Liquid_Src/appdata$Purchase, 2)
appdata$Non_Liquid_Src_Pct <- round(appdata$Non_Liquid_Src/appdata$Purchase, 2)

#networth
appdata <- rename(appdata, Cash = SUIT45)
appdata$Cash <- as.numeric(as.character(appdata$Cash))
appdata <- rename(appdata, Checking = SUIT46)
appdata$Checking <- as.numeric(as.character(appdata$Checking))
appdata <- rename(appdata, CD = SUIT47)
appdata$CD <- as.numeric(as.character(appdata$CD))
appdata <- rename(appdata, IRA = SUIT48)
appdata$IRA <- as.numeric(as.character(appdata$IRA))
appdata <- rename(appdata, Stocks_Bonds = SUIT49)
appdata$Stocks_Bonds <- as.numeric(as.character(appdata$Stocks_Bonds))
appdata <- rename(appdata, MF = SUIT50)
appdata$MF <- as.numeric(as.character(appdata$MF))
appdata <- rename(appdata, Annuities = SUIT51)
appdata$Annuities <- as.numeric(as.character(appdata$Annuities))
appdata <- rename(appdata, Life_Ins = SUIT52)
appdata$Life_Ins <- as.numeric(as.character(appdata$Life_Ins))
appdata <- rename(appdata, Other_Liq = SUIT53)
appdata$Other_Liq <- as.numeric(as.character(appdata$Other_Liq))

appdata$Tot_Liq_Assets <- appdata$Cash + 
  appdata$Checking + appdata$CD + 
  appdata$IRA + appdata$Stocks_Bonds + 
  appdata$MF + appdata$Annuities + 
  appdata$Life_Ins + appdata$Other_Liq

appdata <- rename(appdata, Val_of_Home = SUIT56)
appdata$Val_of_Home <- as.numeric(as.character(appdata$Val_of_Home))
appdata <- rename(appdata, Other_RE = SUIT57)
appdata$Other_RE <- as.numeric(as.character(appdata$Other_RE))
appdata <- rename(appdata, IRA_under = SUIT58)
appdata$IRA_under <- as.numeric(as.character(appdata$IRA_under))
appdata <- rename(appdata, Class_B_MF = SUIT59)
appdata$Class_B_MF <- as.numeric(as.character(appdata$Class_B_MF))
appdata <- rename(appdata, Gold = SUIT60)
appdata$Gold <- as.numeric(as.character(appdata$Gold))
appdata <- rename(appdata, Ann_with_Pen = SUIT61)
appdata$Ann_with_Pen <- as.numeric(as.character(appdata$Ann_with_Pen))
appdata <- rename(appdata, Life_with_Pen = SUIT62)
appdata$Life_with_Pen <- as.numeric(as.character(appdata$Life_with_Pen))
appdata <- rename(appdata, Other_Non_Liq = SUIT63)
appdata$Other_Non_Liq <- as.numeric(as.character(appdata$Other_Non_Liq))
appdata$Other_Non_Liq[is.na(appdata$Other_Non_Liq)] <- 0

appdata$Tot_Non_Liq_Assets <- appdata$Val_of_Home + appdata$Other_RE + 
  appdata$IRA_under + appdata$Class_B_MF + appdata$Gold + 
  appdata$Ann_with_Pen + appdata$Life_with_Pen + appdata$Other_Non_Liq

appdata$Tot_Assets <- appdata$Tot_Liq_Assets + appdata$Tot_Non_Liq_Assets

#size of policy - source of funds - analysis
annuities <- select(appdata, 
                    TransIdentifier, 
                    Liquid_Src, 
                    Non_Liquid_Src, 
                    Liquid_Src_Pct, 
                    Non_Liquid_Src_Pct, 
                    Purchase)

annuities_summary <- summarise(annuities,
          Cases = n(),
          Total_Premium = sum(annuities$Purchase,na.rm=TRUE),
          Avg_Premium = round(mean(annuities$Purchase),0),
          Med_Premium = round(median(annuities$Purchase),0))

annuities_summary <- t(annuities_summary)

print(xtable::xtable(annuities_summary, digits=c(0,0)),type="html",html.table.attributes="border=1")

ggplot(data=annuities,
       aes(Purchase)) + geom_histogram(binwidth = 10000) + xlim(-15000, 200000) + xlab("Premiums per Contract")
```

## Net Worth of Consumers

A few customers reported very large networths and pushed the average networth to $1.5 million. We think the median networth of slightly less than $1 million - $995,000 - presents a truer picture. Roughly half the assets are liquid and the other half is illiquid.
```{r results='asis', echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

#Net worth analysis
networth <- select(appdata, TransIdentifier, Tot_Liq_Assets, Tot_Non_Liq_Assets, Tot_Assets)
networth_summary <- summarise (networth,
                               mean_assets = round(mean(networth$Tot_Assets, na.rm=TRUE),0),
                               mean_liq_assets = round(mean(networth$Tot_Liq_Assets,na.rm=TRUE),0),
                               mean_non_liq_assets = round(mean(networth$Tot_Non_Liq_Assets,na.rm=TRUE),0),
                               median_assets = round(median(networth$Tot_Assets, na.rm=TRUE),0),
                               median_liq_assets = round(median(networth$Tot_Liq_Assets,na.rm=TRUE),0),
                               median_non_liq_assets = round(median(networth$Tot_Non_Liq_Assets,na.rm=TRUE),0)
)
networth_summary <- t(networth_summary)
print(xtable::xtable(networth_summary, digits=c(0,0)),type="html",html.table.attributes="border=1")

ggplot(data=networth, 
       aes(Tot_Assets)) + geom_histogram(binwidth = 100000) + xlim(0,3000000) + xlab("Net Worth of Policyholders")
```

##Source of Net Worth

The largest source of net worth reported by clients was their home, their qualified retirement plan, and their checking or money market account, in that order. The vast majority of the money used to purchase the annuity came from liquid sources.

```{r results='asis', echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

source_of_funds <-summarise(annuities,
          Avg_Liq_Src = round(mean(annuities$Liquid_Src_Pct, na.rm=TRUE),2),
          Avg_Non_Liq_Src = round(mean(annuities$Non_Liquid_Src_Pct, na.rm=TRUE),2))

print(xtable::xtable(source_of_funds),type="html",html.table.attributes="border=1")
```


####Liquid Assets

Most of the liquid net worth comes first from a qualified plan (i.e. IRA, 401(k)) and then from a checking or money market account. Some large outliers in all categories distort the average amount.

```{r echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

#Source of networth
networth_source_liq <- summarise (appdata, 
                                  Value = "Median",
                                  Cash = round(median(appdata$Cash, na.rm=TRUE),0),
                                  Checking = round(median(appdata$Checking, na.rm=TRUE),0),
                                  CDs = round(median(appdata$CD, na.rm=TRUE),0),
                                  IRAs = round(median(appdata$IRA, na.rm=TRUE),0),
                                  Stocks_Bonds = round(median(appdata$Stocks_Bonds, na.rm=TRUE),0),
                                  Mutual_Funds = round(median(appdata$MF, na.rm=TRUE),0),
                                  Annuities = round(median(appdata$Annuities, na.rm=TRUE),0),
                                  Life_Ins = round(median(appdata$Life_Ins, na.rm=TRUE),0),
                                  Other = round(median(appdata$Other_Liq, na.rm=TRUE),0))


networth_source_liq2 <- summarise (appdata, 
                                   Value = "Average",
                                  Cash = round(mean(appdata$Cash, na.rm=TRUE),0),
                                  Checking = round(mean(appdata$Checking, na.rm=TRUE),0),
                                  CDs = round(mean(appdata$CD, na.rm=TRUE),0),
                                  IRAs = round(mean(appdata$IRA, na.rm=TRUE),0),
                                  Stocks_Bonds = round(mean(appdata$Stocks_Bonds, na.rm=TRUE),0),
                                  Mutual_Funds = round(mean(appdata$MF, na.rm=TRUE),0),
                                  Annuities = round(mean(appdata$Annuities, na.rm=TRUE),0),
                                  Life_Ins = round(mean(appdata$Life_Ins, na.rm=TRUE),0),
                                  Other = round(mean(appdata$Other_Liq, na.rm=TRUE),0))

networth_source_liq <- union (networth_source_liq, networth_source_liq2)

networth_source_liq <-t(networth_source_liq)  

networth_source_liq

```

####Non-Liquid Assets

The house is typically the major non-liquid asset reported by clients.

```{r  echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

#non-liquid assets
networth_source_nonliq <- summarise (appdata, 
                                  Value = "Median",
                                  Val_of_Home = round(median(appdata$Val_of_Home, na.rm=TRUE),0),
                                  Other_RE = round(median(appdata$Other_RE, na.rm=TRUE),0),
                                  IRA_under = round(median(appdata$IRA_under, na.rm=TRUE),0),
                                  Class_B_MF = round(median(appdata$Class_B_MF, na.rm=TRUE),0),
                                  Gold = round(median(appdata$Gold, na.rm=TRUE),0),
                                  Ann_with_Pen = round(median(appdata$Ann_with_Pen, na.rm=TRUE),0),
                                  Life_with_Pen = round(median(appdata$Life_with_Pen, na.rm=TRUE),0),
                                  Other_Non_Liq = round(median(appdata$Other_Non_Liq, na.rm=TRUE),0))


networth_source_nonliq2 <- summarise (appdata, 
                                   Value = "Average",
                                   Val_of_Home = round(mean(appdata$Val_of_Home, na.rm=TRUE),0),
                                   Other_RE = round(mean(appdata$Other_RE, na.rm=TRUE),0),
                                   IRA_under = round(mean(appdata$IRA_under, na.rm=TRUE),0),
                                   Class_B_MF = round(mean(appdata$Class_B_MF, na.rm=TRUE),0),
                                   Gold = round(mean(appdata$Gold, na.rm=TRUE),0),
                                   Ann_with_Pen = round(mean(appdata$Ann_with_Pen, na.rm=TRUE),0),
                                   Life_with_Pen = round(mean(appdata$Life_with_Pen, na.rm=TRUE),0),
                                   Other_Non_Liq = round(mean(appdata$Other_Non_Liq, na.rm=TRUE),0))

networth_source_nonliq <- union (networth_source_nonliq, networth_source_nonliq2)

networth_source_nonliq <-t(networth_source_nonliq)  
networth_source_nonliq
```


##Home Values

The average value of the home was close to $300,000. The median was exactly $230,000.

```{r results='asis',  echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

#value of home - analysis
homedata <- select(appdata, TransIdentifier, Val_of_Home)

homedata_summary <- summarise(homedata,
          minimum = round(min(homedata$Val_of_Home),0),
          mean = round(mean(homedata$Val_of_Home),0),
          median = round(median(homedata$Val_of_Home),0),
          maximum = round(max(homedata$Val_of_Home),0))

homedata_summary <- t(homedata_summary)

print(xtable::xtable(homedata_summary, digits=c(0,0)),type="html",html.table.attributes="border=1")

ggplot(data=homedata, 
       aes(Val_of_Home)) + geom_histogram(binwidth = 50000) + xlim(-100, 1000000) + xlab("Value of Home")


```

##Age

We received the age of owners for the latest MYGA program. The average age of our client is 68 and the oldest was 90. 

```{r results='asis',  echo=FALSE, }

wave2 <- merge(appdata, dell)
wave2 <- merge(wave2,fgl)
wave2 <- subset(wave2, Issued == "Yes")
wave2$StatusDate <-as.Date(as.character(wave2$StatusDate), format = "%m/%d/%y")
wave2$DateCreated <-as.Date(as.character(wave2$StatusDate), format = "%m/%d/%y")
wave2$Amount <- as.numeric(as.character(wave2$Amount))
wave2$AgentID <- as.character(wave2$AgentID)

#average age
average_age <- summarise(wave2,
                         Avg_age = round(mean(Insured.Age),1),
                         Med_age = round(median(Insured.Age),1),
                         Max_age = max(Insured.Age)
                         )

print(xtable::xtable(average_age, digits=c(0,1,0,0)),type="html",html.table.attributes="border=1")

ggplot(data=wave2, 
       aes(Insured.Age)) + 
  geom_histogram(binwidth = 5) + xlim(40,100) + xlab("Age of Clients")
```

We saw little difference in average case size in any age band.

```{r results='asis',  echo=FALSE, }

#customers by age decile
wave2$Decile_Age <- ntile(wave2$Insured.Age,10)
customers_decile_age <- group_by(wave2, Decile_Age)
customers_decile_age <- summarise(customers_decile_age,
                                 Min_age = min(Insured.Age),
                                 Max_age = max(Insured.Age),
                                 Avg_case = round(mean(Purchase),0),
                                 Total_sales = sum(Purchase),
                                 Tot_Cases = n()
)

p <- ggplot(data=customers_decile_age, aes(Decile_Age, Avg_case)) 
p <- p + geom_bar(stat = "identity") + xlab("Decile") + ylab("Average Premium")
p <- p + ggtitle("Total Sales by Decile")
p


print(xtable::xtable(customers_decile_age, digits=c(0,0,0,0,0,0,0)),type="html",html.table.attributes="border=1")
```

##Discretionary Income

We ask applicants for their monthly income and monthly expenses. The difference or median discretionary income to spend is $2,500.

```{r results='asis',  echo=FALSE, }
#Income & expense analysis - analysis
avg_monthly_cashflow <- select (appdata, TransIdentifier, Monthly_Income, Monthly_Expense, Monthly_Discretionary)

discretionary <-summarise(avg_monthly_cashflow,
          minimum_discr = round(min(avg_monthly_cashflow$Monthly_Discretionary),0),
          mean_discr = round(mean(avg_monthly_cashflow$Monthly_Discretionary),0),
          median_discr = round(median(avg_monthly_cashflow$Monthly_Discretionary),0),
          maximum_discr = round(max(avg_monthly_cashflow$Monthly_Discretionary),0))
discretionary <- t(discretionary)

print(xtable::xtable(discretionary, digits=c(0,0)),type="html",html.table.attributes="border=1")

ggplot(data=avg_monthly_cashflow, 
       aes(Monthly_Discretionary)) + 
  geom_histogram(binwidth = 1000) + xlim(-500,20000) + xlab("Monthly Discretionary Income")
```

##Work Status

Close to 70% owners as well as any joint owners reported they were "retired." Slightly more than 30% indicated they were employed.

####Owner

```{r results='asis',  echo=FALSE, }

ct = c(1, 2, 3, 4, 5)
status = c("Retired", "Employed", "Unemployed", "Other", "NA")
work_key = data.frame(ct, status)
owner_status <- count (appdata, ct = SUIT01)
owner_status <- mutate(owner_status, pct =round(n / sum(n), 2))
owner_status_final <- merge(work_key, owner_status)
print(xtable::xtable(owner_status_final),type="html",html.table.attributes="border=1")

```
####Joint Owner

```{r results='asis',  echo=FALSE, }

ct = c(1, 2, 3, 4)
status = c("Retired", "Employed", "Unemployed", "Other")
work_key = data.frame(ct, status)
jt_owner_status <- count (appdata, ct = SUIT03)
jt_owner_status <- merge(work_key,jt_owner_status)
jt_owner_status <- mutate(jt_owner_status, pct =round(n / sum(n), 2))
#jt_owner_status_final <- merge(work_key, jt_owner_status)
print(xtable::xtable(jt_owner_status),type="html",html.table.attributes="border=1")

```

##Gender

In the last wave of sales, 45% of customers were women, 55% were men. Cases sold to men were slightly higher larger than those sold to women. 

```{r results='asis',  echo=FALSE, }

#Sex analysis

customers_sex <- group_by(wave2, Insured.Gender)
customers_sex <- summarise(customers_sex,
                           Avg_age = round(mean(Insured.Age),0),
                           Avg_case = round(mean(Purchase),0),
                           Total_sales = sum(Purchase),
                           Pct_sales = Total_sales / sum(wave2$Purchase),
                           Tot_Cases = n(),
                           Pct_Cases = Tot_Cases / length(wave2$TransIdentifier),
                           Mean_Home = round(mean(Val_of_Home),0),
                           Mean_Assets = round(mean(Tot_Assets, na.rm=TRUE),0)
)

print(xtable::xtable(customers_sex, digits=c(0,0,0,0,0,2,0,2,0,0)),type="html",html.table.attributes="border=1")
```


##Impact of Accepting 1035s

We launched our second online MYGA program begining November 30, 2015 as cash-only offer. On January 20, 2016, we began accepting 1035 exchanges. The change in process did not appear to impact the size of cases. However, the daily sales level picked up substantially after the announcement. The rate hike from 3% to 3.15% on 2/26 created the very large spike in March.

```{r results='asis',  echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)



#wave3 <- select(wave2, TransIdentifier, Liquid_Src, Non_Liquid_Src,Amount, Purchase) 
#wave3$difference <- round(wave3$Amount,0) - round(wave3$Purchase, 0)
#wave4 <- subset(wave3, Amount != Purchase)
#wave4 <- select(wave4, TransIdentifier, Liquid_Src, Non_Liquid_Src,Amount, Purchase)

myga1035pre <- subset(wave2, StatusDate < "2016-01-15")
myga1035pre <- select(myga1035pre, 
                      TransIdentifier, 
                      StatusDate, 
                      Purchase, 
                      Tot_Assets )

myga1035pre <- summarise (myga1035pre,
  Time = "Pre-1035s",
  Cases = n(),
  Avg_Premium = round(mean(myga1035pre$Purchase, na.rm=TRUE),0),
  Med_Premium = round(median(myga1035pre$Purchase, na.rm=TRUE),0),
  Avg_Assets = round(mean(myga1035pre$Tot_Assets, na.rm=TRUE),0),
  Med_Assets = round(median(myga1035pre$Tot_Assets, na.rm=TRUE),0)
)

myga1035post <- subset(wave2, StatusDate > "2016-01-15")
myga1035post <- select(myga1035post, 
                       TransIdentifier, 
                       StatusDate,
                       Purchase,
                       Tot_Assets
                       )

myga1035post <- summarise(myga1035post,
  Time = "Post-1035s",
  Cases = n(),
  Avg_Premium = round(mean(myga1035post$Purchase),0),
  Med_Premium = round(median(myga1035post$Purchase),0),
  Avg_Assets = round(mean(myga1035post$Tot_Assets, na.rm=TRUE),0),
  Med_Assets = round(median(myga1035post$Tot_Assets, na.rm=TRUE),0)
)

myga1035analysis <- union(myga1035pre, myga1035post)

print(xtable::xtable(myga1035analysis, digits=c(0,0,0,0,0,0,0)),type="html",html.table.attributes="border=1")



```


That said, accepting 1035 exchanges allowed us to increase the size of cases by approximately 20%.

```{r results='asis',  echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

#1035 analysis

cases_1035 <- group_by(wave2, Is.1035)
cases_1035 <- summarise(cases_1035,
          Cases = n(),
          Total_Premium = sum(Purchase,na.rm=TRUE),
          Avg_Premium = round(mean(Purchase),0),
          Med_Premium = round(median(Purchase),0),
          Avg_Liq_Src = round(mean(Liquid_Src_Pct, na.rm=TRUE),2),
          Avg_Non_Liq_Src = round(mean(Non_Liquid_Src_Pct, na.rm=TRUE),2))

print(xtable::xtable(cases_1035, digits=c(0,0,0,0,0,0,2,2)),type="html",html.table.attributes="border=1")

```

##Role of the Agent
It appears that agents generally sold the same size of case during the last special. No segment of agents seems to have consistently sold larger cases than the overall population.

```{r  echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

#agent concentration
agents <- group_by(wave2, AgentID)
agents <- summarise(agents,
                    Cases = n(),
                    Large_cases = length(which(Purchase > 150000)),
                    Avg_case_size = mean(Purchase),
                    Med_case_size = median(Purchase),
                    St_dev = sd(Purchase),
                    Total_sales = sum(Purchase)
                    )
agents_summary <- summarize(agents,
                            Avg_cases = mean(Cases),
                            Avg_case_size = mean(Avg_case_size)
)



p <- ggplot(data = agents, aes(Avg_case_size,St_dev)) 
p <- p + geom_point() + xlab("Avg Premium Per Case")
p <- p + ylab("Standard Deviation of Case Size") 
p <- p + ggtitle("Mix of Cases Submitted By Agent")
p <- p + geom_smooth(method='lm')
p

ag_regression <- lm(agents$St_dev~agents$Avg_case_size)
lm(agents$St_dev~agents$Avg_case_size)
summary(ag_regression)


p <- ggplot(data = agents, aes(Cases,Avg_case_size)) 
p <- p + geom_point() + xlab("Number of Cases")
p <- p + ylab("Standard Deviation of Case Size") 
p <- p + ggtitle("Mix of Cases Submitted By Agent")
p <- p + geom_smooth(method='lm')
p
ag_regression <- lm(agents$St_dev~agents$Cases)
lm(agents$St_dev~agents$Cases)
summary(ag_regression)
```

##Concentration of Business

####Distribution by Agent Sales Volume

```{r results='asis',  echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

#agents by decile
agents$Decile_Sales <- ntile(agents$Total_sales,10)
agents$Decile_Cases <- ntile(agents$Cases,10)

agents_decile_sales <- group_by(agents, Decile_Sales)
agents_decile_sales <- summarise(agents_decile_sales,
                                 Avg_case_size = round(mean(Avg_case_size),0),
                                 Med_case_size = round(median(Med_case_size),0),
                                 Total_sales = sum(Total_sales),
                                 Avg_cases = round(mean(Cases),1),
                                 Avg_lg_cases = round(mean(Large_cases),1),
                                 Tot_Cases = sum(Cases),
                                 St_dev = round(mean(St_dev, na.rm = TRUE),0)
                           )

agents_decile_cases <- group_by(agents, Decile_Cases)
agents_decile_cases <- summarise(agents_decile_cases,
                                 Total_cases = sum(Cases),
                                 Avg_cases = round(mean(Cases),1),
                                 Avg_lg_cases = round(mean(Large_cases),1),
                                 Avg_case_size = round(mean(Avg_case_size),0),
                                 Med_case_size = round(median(Med_case_size),0),
                                 Total_sales = sum(Total_sales),
                                 Avg_case_size = round(mean(Avg_case_size),0),
                                 St_dev = round(mean(St_dev, na.rm = TRUE),0)
                                 
)

print(xtable::xtable(agents_decile_sales, caption ="Large cases are greater than $150,000", digits=c(0,0,0,0,0,1,1,0,0)),type="html",html.table.attributes="border=1")
p <- ggplot(data=agents_decile_sales, aes(Decile_Sales, Total_sales)) 
p <- p + geom_bar(stat = "identity") + xlab("Decile") + ylab("Total Sales")
p <- p + ggtitle("Total Sales by Decile")
p

```


####Distribution by Agent Case Volume

```{r results='asis',  echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

print(xtable::xtable(agents_decile_cases,caption ="Large cases are greater than $150,000", digits=c(0,0,0,1,1,0,0,0,0)),type="html",html.table.attributes="border=1")


p <- ggplot(data=agents_decile_cases, aes(Decile_Cases, Total_sales)) 
p <- p + geom_bar(stat = "identity") + xlab("Decile") + ylab("Total Cases")
p <- p + ggtitle("Total Cases by Decile")
p

```

####Multivariate regression model

```{r  echo=FALSE, }
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

model_purchase <- select(wave2,
                         Purchase,
                         Is.1035,
                         Insured.Gender,
                         Tot_Liq_Assets,
                         Val_of_Home,
                         Checking,
                         CD,
                         Insured.Age,
                         Tot_Assets)



model_purchase$Sex <-  ifelse(model_purchase$Insured.Gender == "M", 1, 0)


#strongest fit
summary(lm(Purchase ~ Insured.Gender + Is.1035 + Checking, data = model_purchase))

```
